Extended Abstract

### 2021-07-27 paper/paper.tex
Use pseudo BNF for kinding judgment

Both types and usage annotations contain metavariables.
We use a common set of metavariables for both --- this makes their handling uniform.
A context of kinds \(\gamma\) keeps track of whether a metavariable is of type kind $\ktype$ or usage annotation kind $\kusage$.
We define $\tvar{\gamma}{k}$ as the set of variables of kind \(k\) in a kinding context \(\gamma\), and $\tkind{\gamma}{k}$ as the set of types \(\ktype\) and usage annotations \(\kusage\) (we omit unit and sum types and define $\tzero$, $\tone$, $\tomega$ at once for brevity):
\begin{mathpar}
  \inferrule {m : \tvar{\gamma}{k}} {\tmvar~m : \tkind{\gamma}{k}}

  \inferrule {
    i : \tkind{\gamma}{\kusage} \\
    o : \tkind{\gamma}{\kusage} \\
    t : \tkind{\gamma}{\ktype}}
  {\tchan~i~o~t : \tkind{\gamma}{\ktype}}

  \inferrule {s : \tkind{\gamma}{\ktype} \\ t : \tkind{\gamma}{\ktype} }
  {\tprod~s~t : \tkind{\gamma}{\ktype}}

  \inferrule { } {\tzero ~|~ \tone ~|~ \tomega : \tkind{\gamma}{\kusage}}
\end{mathpar}
We henceforth use $\ttype{\gamma}$ for $\tkind{\gamma}{\ktype}$ and $\tusage{\gamma}$ for $\tkind{\gamma}{\kusage}$.

>>>>

Both types and usage annotations contain metavariables.
To make their handling uniform we use a common set of metavariables for both.
A context of kinds \(\gamma\) keeps track of whether a metavariable is of type kind $\ktype$ or usage annotation kind $\kusage$.
Variable references $m$ are of type $\tvar{\gamma}{k}$: the set of variables of kind \(k\) in a kinding context \(\gamma\).
Usage annotations $i$ and $o$ are of type $\tkind{\gamma}{\kusage}$, and types $s$ and $t$ of type $\tkind{\gamma}{\ktype}$.
We henceforth abbreviate $\tkind{\gamma}{\ktype}$ as $\ttype{\gamma}$ and $\tkind{\gamma}{\kusage}$ as $\tusage{\gamma}$.
\[
\begin{aligned}[c]
  i ~ o :=& ~ \tmvar_{\kusage} ~ m ~|~ \tzero ~|~ \tone ~|~ \tomega \\
  s ~ t :=& ~ \tmvar_{\ktype} ~ m ~|~ \tunit ~|~ \tchan ~ i ~ o ~ t ~|~ \tprod ~ s ~ t ~|~ \tsum ~ s ~ t
\end{aligned}
\]
